Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-02-06 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny

\maketitle
\section{Introduction\label{s:introduction}}
Water exchange is essential for a living cell to adapt to its
environment over a wide range of time
scales~\cite{CadartVenkovaRechoEtAl2019_NaturePhys,
AlbertsMolecularBiology, YangMaVerkman2001_JBC,
SugieIntaglietta2018_AmJPhysiolHCP,
SaadounPapadopoulosWatanabeEtAl2005_JCS, Verkman2008_JMM,
BerthaudEtAl2016_SM, Keren2011_EurBJ, TaloniKardashSalmanEtAl2015_PRL}.  
%
%Water permeation across the cell membrane due to an osmotic shock has been well studied \cite{AlbertsMolecularBiology}. 
Recent findings confirm that both osmotic and mechanical stresses
contribute to significant water permeation for cells to migrate under
strong confinement~\cite{JiangSun2013_BJ, StrokaJiangChenEtAl2014_Cell,
LiMoriSun2015_PRL, yao-mor2017}, leading to a dynamic surface-to-volume
ratio of a migrating cell. While stress-induced release of messengers in
cells has been well-studied~\cite{Wan2008_PNAS, ForsythWan2011_PNAS, 
Russell-PuleriPazAdams2016_AJHCP, ZhangShenHoganBarakatMisbah2018_BJ,
GordonShimmelFrye2020_FP},
%osmotic effects on cellular dynamics have been well studied
%\cite{AlbertsMolecularBiology}, 
mechanically induced water permeation is often associated with membrane
poration or rupture under extreme
stresses~\cite{HarmanBertrandJoos2017_CJP,
RazizadehNikfarPaulLiu2020_BJ}. In this work we use modeling and direct
numerical simulations to show that, over the appropriate time scales or
under strong confinement, the intrinsic membrane permeability to water
can give rise to significantly distinct hydrodynamics of a semipermeable
vesicle without poration or rupture in the lipid bilayer membrane.

>>>>

\maketitle
\section{Introduction\label{s:introduction}}
Water exchange is essential for a living cell to adapt to its
environment over a wide range of time
scales~\cite{CadartVenkovaRechoEtAl2019_NaturePhys,
AlbertsMolecularBiology, YangMaVerkman2001_JBC,
SugieIntaglietta2018_AmJPhysiolHCP,
SaadounPapadopoulosWatanabeEtAl2005_JCS, Verkman2008_JMM,
BerthaudEtAl2016_SM, Keren2011_EurBJ, TaloniKardashSalmanEtAl2015_PRL}.  
%
%Water permeation across the cell membrane due to an osmotic shock has been well studied \cite{AlbertsMolecularBiology}. 
Recent findings confirm that both osmotic and mechanical stresses
contribute to significant water permeation for cells to migrate under
strong confinement~\cite{JiangSun2013_BJ, StrokaJiangChenEtAl2014_Cell,
LiMoriSun2015_PRL, yao-mor2017}, leading to a dynamic surface-to-volume
ratio of a migrating cell. While stress-induced release of messengers in
cells has been well-studied~\cite{Wan2008_PNAS, ForsythWan2011_PNAS, 
Russell-PuleriPazAdams2016_AJHCP, ZhangShenHoganBarakatMisbah2018_BJ,
GordonShimmelFrye2020_FP},
%osmotic effects on cellular dynamics have been well studied
%\cite{AlbertsMolecularBiology}, 
mechanically induced water permeation is often associated with membrane
poration or rupture under extreme
stresses~\cite{HarmanBertrandJoos2017_CJP,
RazizadehNikfarPaulLiu2020_BJ}. In this work we use modeling and direct
numerical simulations to show that, over the appropriate time scales or
under strong confinement, the intrinsic membrane permeability to water
can give rise to significantly distinct hydrodynamics of a semipermeable
vesicle.
